The Mass Distribution of Stellar-Mass Black Holes

### 2010-10-26 paper.tex
Plot edits (partial) for Vicky.

\begin{figure}
  \begin{center}
    \plottwo{plots/dist-parametric}{plots/dist-non-parametric}
  \end{center}
  \caption{\label{fig:dists} The median (solid line), 10\% (lower
    dashed line) and 90\% (upper dashed line) values of the black hole
    mass distribution, $p(M|\theta)$, at various masses implied by the
    posterior $p(\theta|d)$ for the models discussed in Sections
    \ref{sec:parametric-models} and \ref{sec:non-parametric-models}.
    These distributions use only the 15 low-mass observations in Table
    \ref{tab:sources} (the complete sample is analyzed in Section
    \ref{sec:higher-mass}).  Error bars span the 10\% to 90\% range.
    Note that these ``distributions of distributions'' are not
    necessarily normalized, and need not be shaped like the underlying
    model distributions.}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/power-law}
  \end{center}
  \caption{\label{fig:power-law} A histogram of the marginalized
    distribution for the three parameters $\Mmin$, $\Mmax$, and
    $\alpha$ from the power-law model.  The marginalized distribution
    for $\alpha$ is broad, with $-11.8 < \alpha < 6.8$ enclosing 90\%
    of the probability.  We have $p(\alpha < 0) = 0.6$; the median
    value is $\alpha = -3.35$.  The broad distribution for $\alpha$
    (and the other parameters) is due to correlations between the
    parameters discussed in the main text; see Figure
    \ref{fig:power-law-2D}.}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/exp-cutoff}
  \end{center}
  \caption{\label{fig:exp-marginal} The distribution of scale masses,
    $M_0$, and minimum masses, $\Mmin$, both measured in units of a
    solar mass for the exponential underlying mass distribution
    defined in Equation \eqref{eq:exp-def}.  The median scale mass is
    $M_0 = 1.55$, and $0.78 \leq M_0 \leq 3.25$ with 90\%
    confidence.}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/gaussian}
  \end{center}
  \caption{\label{fig:gaussian} Marginalized posterior distributions
    for the mean $\mu$ and standard deviation $\sigma$ (both in solar
    masses) for the Gaussian underlying mass distribution defined in
    Equation \eqref{eq:gaussian-def}.  The peak of the Gaussian,
    $\mu$, is constrained in $6.63 \leq \mu \leq 8.08$ with 90\%
    confidence.}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/two-gaussian}
  \end{center}
  \caption{\label{fig:two-gaussian} The marginal distributions for the
    five parameters of the two-Gaussian model.  We have $\alpha > 0.8$
    with 62\% probability, favoring the first of the two Gaussians.
    The distributions for $\mu_1$ and $\sigma_1$ are similar to those
    of the single Gaussian model displayed in Figure
    \ref{fig:gaussian}; the second Gaussian's parameter distributions
    are much broader (recall that we constrain $\mu_2 > \mu_1$).  The
    second Gaussian is attempting to fit the tail of the mass samples.
    The extra degrees of freedom in the distribution from the second
    Gaussian do not provide enough extra fitting power to compensate
    for the increase in parmeter space, however: the two-Gaussian
    model is disfavored relative to the single Gaussian by a factor of
    $4.7$ on this dataset (see Sections \ref{sec:model-selection} and
    \ref{sec:lower-mass-model-selection} for discussion).}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/log-normal}
  \end{center}
  \caption{\label{fig:log-normal} Marginalized distributions of the
    mean mass, $\langle M \rangle$, and standard deviation of the
    mass, $\sigma_M$, for the log-normal model in Section
    \ref{sec:log-normal}.  The distributions are similar to the
    distributions of $\mu$ and $\sigma$ in the Gaussian model of
    Section \ref{sec:gaussian}.}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plottwo{plots/dist-parametric-high}{plots/dist-non-parametric-high-mass}
  \end{center}
  \caption{\label{fig:high-mass-dists} The median (solid line), 10\%
    (lower dashed line), and 90\% (upper dashed line) values of the
    black hole mass distribution, $p(M|\theta)$, at various masses
    implied by the posterior $p(\theta|d)$ for the models discussed in
    Sections \ref{sec:parametric-models} and
    \ref{sec:non-parametric-models}.  These distributions use the
    complete sample of 20 observations in Table \ref{tab:sources},
    including the higher-mass, wind-fed systems.  Error bars span the
    10\% to 90\% range.  Note that these ``distributions of
    distributions'' are not necessarily normalized, and need not be
    ``shaped'' like the underlying model distributions.  Compare to
    Figure \ref{fig:dists}, which includes only the low-mass systems
    in the analysis.  Including the higher-mass systems tends to widen
    the distribution toward the high-mass end and, in models that
    allow it, produce a second, higher-mass peak in addition to the
    one in Figure \ref{fig:dists}. }
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/power-law-high}
  \end{center}
  \caption{\label{fig:power-law-high} A histogram of the marginalized
    distribution for the three parameters $\Mmin$, $\Mmax$, and
    $\alpha$ from the power-law model including the higher-mass
    samples in the MCMC.  The distribution for $\Mmax$ is quite broad
    because the best fit power laws slope downward ($\alpha < 0$),
    making this parameter less relevant.  The range $-5.05 \leq \alpha
    \leq -1.77$ encloses 90\% of the probability; the median value of
    $\alpha$ is -3.23.  The presence of the higher-mass samples in the
    analysis produces a distinctive tail, eliminating the correlations
    discussed in Section \ref{sec:power-law} and displayed in Figure
    \ref{fig:power-law-2D} for the lower-mass subset of the
    observations. }
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plottwo{plots/mmin-parametric}{plots/mmin-non-parametric}
  \end{center}
  \caption{\label{fig:min-mass} The distributions for the minimum
    black hole mass calculated from the MCMC samples for the models in
    Section \ref{sec:models} applied to the lower-mass systems.  The
    minimum black hole mass is defined as the 1\% mass quantile.  For
    the most favored models, the power-law and Gaussian, the 90\%
    confidence limit on the minimum black hole mass is 4.3 $\Msun$ and
    2.9 $\Msun$, respectively.}
\end{figure}

@@

\begin{figure}
\begin{center}
    \plottwo{plots/mmin-parametric-high}{plots/mmin-non-parametric-high}
  \end{center}
  \caption{\label{fig:high-min-mass} The distributions for the minimum
    black hole mass calculated from the MCMC samples for the models in
    Section \ref{sec:models} using the complete sample of systems.
    The minimum black hole mass is defined as the 1\% mass quantile.
    For the most favored model, the exponential, the 90\% confidence
    limit on the minimum black hole mass is 4.5 $\Msun$.}
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    \plotone{plots/dist}
  \end{center}
  \caption{\label{fig:dists} The median (solid line), 10\% (lower
    dashed line) and 90\% (upper dashed line) values of the black hole
    mass distribution, $p(M|\theta)$, at various masses implied by the
    posterior $p(\theta|d)$ for the models discussed in Sections
    \ref{sec:parametric-models} and \ref{sec:non-parametric-models}.
    These distributions use only the 15 low-mass observations in Table
    \ref{tab:sources} (the complete sample is analyzed in Section
    \ref{sec:higher-mass}).  Note that these ``distributions of
    distributions'' are not necessarily normalized, and need not be
    shaped like the underlying model distributions.}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/power-law}
  \end{center}
  \caption{\label{fig:power-law} Histograms of the marginalized
    distribution for the three parameters $\Mmin$, $\Mmax$, and
    $\alpha$ from the power-law model.  The marginalized distribution
    for $\alpha$ is broad, with $-11.8 < \alpha < 6.8$ enclosing 90\%
    of the probability.  We have $p(\alpha < 0) = 0.6$; the median
    value is $\alpha = -3.35$.  The broad distribution for $\alpha$
    (and the other parameters) is due to correlations between the
    parameters discussed in the main text; see Figure
    \ref{fig:power-law-2D}.}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/exp-cutoff}
  \end{center}
  \caption{\label{fig:exp-marginal} The distribution of scale masses,
    $M_0$ (dashed histogram), and minimum masses, $\Mmin$ (solid
    histogram), both measured in units of a solar mass for the
    exponential underlying mass distribution defined in Equation
    \eqref{eq:exp-def}.  The median scale mass is $M_0 = 1.55$, and
    $0.78 \leq M_0 \leq 3.25$ with 90\% confidence.}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/gaussian}
  \end{center}
  \caption{\label{fig:gaussian} Marginalized posterior distributions
    for the mean, $\mu$ (solid histogram), and standard deviation,
    $\sigma$ (dashed histogram), both in solar masses for the Gaussian
    underlying mass distribution defined in Equation
    \eqref{eq:gaussian-def}.  The peak of the Gaussian, $\mu$, is
    constrained in $6.63 \leq \mu \leq 8.08$ with 90\% confidence.}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/two-gaussian}
  \end{center}
  \caption{\label{fig:two-gaussian} The marginal distributions for the
    five parameters of the two-Gaussian model.  The top panel is
    $\mu_1$ (solid histogram) and $\sigma_1$ (dashed histogram), the
    middle panel is $\mu_2$ (solid histogram) and $\sigma_2$ (dashed
    histogram), and the bottom panel is $\alpha$. We have $\alpha >
    0.8$ with 62\% probability, favoring the first of the two
    Gaussians.  The distributions for $\mu_1$ and $\sigma_1$ are
    similar to those of the single Gaussian model displayed in Figure
    \ref{fig:gaussian}; the second Gaussian's parameter distributions
    are much broader (recall that we constrain $\mu_2 > \mu_1$).  The
    second Gaussian is attempting to fit the tail of the mass samples.
    The extra degrees of freedom in the distribution from the second
    Gaussian do not provide enough extra fitting power to compensate
    for the increase in parmeter space, however: the two-Gaussian
    model is disfavored relative to the single Gaussian by a factor of
    $4.7$ on this dataset (see Sections \ref{sec:model-selection} and
    \ref{sec:lower-mass-model-selection} for discussion).}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/log-normal}
  \end{center}
  \caption{\label{fig:log-normal} Marginalized distributions of the
    mean mass, $\langle M \rangle$ (solid histogram), and standard
    deviation of the mass, $\sigma_M$ (dashed histogram), for the
    log-normal model in Section \ref{sec:log-normal}.  The
    distributions are similar to the distributions of $\mu$ and
    $\sigma$ in the Gaussian model of Section \ref{sec:gaussian}.}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/dist-high}
  \end{center}
  \caption{\label{fig:high-mass-dists} The median (solid line), 10\%
    (lower dashed line), and 90\% (upper dashed line) values of the
    black hole mass distribution, $p(M|\theta)$, at various masses
    implied by the posterior $p(\theta|d)$ for the models discussed in
    Sections \ref{sec:parametric-models} and
    \ref{sec:non-parametric-models}.  These distributions use the
    complete sample of 20 observations in Table \ref{tab:sources},
    including the higher-mass, wind-fed systems.  Note that these
    ``distributions of distributions'' are not necessarily normalized,
    and need not be ``shaped'' like the underlying model
    distributions.  Compare to Figure \ref{fig:dists}, which includes
    only the low-mass systems in the analysis.  Including the
    higher-mass systems tends to widen the distribution toward the
    high-mass end and, in models that allow it, produce a second,
    higher-mass peak in addition to the one in Figure
    \ref{fig:dists}. }
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/power-law-high}
  \end{center}
  \caption{\label{fig:power-law-high} Histograms of the marginalized
    distribution for the three parameters $\Mmin$, $\Mmax$, and
    $\alpha$ from the power-law model including the higher-mass
    samples in the MCMC.  The distribution for $\Mmax$ is quite broad
    because the best fit power laws slope downward ($\alpha < 0$),
    making this parameter less relevant.  The range $-5.05 \leq \alpha
    \leq -1.77$ encloses 90\% of the probability; the median value of
    $\alpha$ is -3.23.  The presence of the higher-mass samples in the
    analysis produces a distinctive tail, eliminating the correlations
    discussed in Section \ref{sec:power-law} and displayed in Figure
    \ref{fig:power-law-2D} for the lower-mass subset of the
    observations. }
\end{figure}

@@

\begin{figure}
  \begin{center}
    \plotone{plots/mmin}
  \end{center}
  \caption{\label{fig:min-mass} The distributions for the minimum
    black hole mass calculated from the MCMC samples for the models in
    Section \ref{sec:models} applied to the lower-mass systems.  The
    minimum black hole mass is defined as the 1\% mass quantile.  For
    the most favored models, the power-law and Gaussian, the 90\%
    confidence limit on the minimum black hole mass is 4.3 $\Msun$ and
    2.9 $\Msun$, respectively.}
\end{figure}

@@

\begin{figure}
\begin{center}
    \plotone{plots/mmin-high}
  \end{center}
  \caption{\label{fig:high-min-mass} The distributions for the minimum
    black hole mass calculated from the MCMC samples for the models in
    Section \ref{sec:models} using the complete sample of systems.
    The minimum black hole mass is defined as the 1\% mass quantile.
    For the most favored model, the exponential, the 90\% confidence
    limit on the minimum black hole mass is 4.5 $\Msun$.}
\end{figure}
